Social Visual Analytics: DevOps for Data Scientists

### 2015-03-23 interviews.tex
a little bit more narrative
long ways to go

\subsection{Sharing of results}
Sharing of notebooks is the core feature of RCloud, and a popular one. Almost
everyone we spoke to praised this feature. By default, all notebooks are
publicly visible in RCloud, and notebooks can be found through the notebook tree
or search.

However, the method for sharing that users mentioned most is by sending links
through email. Clint says, ``I can share it with people and copy it pretty
readily. So if my supervisor wants to see what I've done or QA it, I can just
send her a link.''

``I think the best part about it is how easily you can share code... you can
find a working example, rather than wearing out Google and finding questionable
examples that may or may not work.''

Corey: ``being able to share notebooks or codes, or collaborate on something,
easily being able to share that information. That's an obvious advantage and
nice to have.''

Raif: ``I've been sharing my notebooks in order for other people to see what
I've done. It's very convenient for that purpose, I would say'' ``we haven't
been editing them together, but we've been just sharing, and then I've been
looking at these things that other people do. So there's no collaborative aspect
of it, like developing the code, but there's like sharing aspects for other
people to see and for me to see other people's notebooks'' ``there already is
some person who has done something similar, and then you're able to just edit
that, and that's saved a lot of work time for me''

Taylor: ``I use it more for sharing code with other people, and for doing
tutorials for iotools or hmr or explaining'' ``a lot of times I'll share the
code, because I'm doing so much package development. I want people to see how
the package works, so I clearly want them to see the code… I kind of write it
just like I would write GitHub Markdown, where you have little code snippets and
text, but RCloud lets me actually run the snippets'' with results.

@@

Rick: ``I like being able to look at other people's notebooks.''

@@

Taylor: ``I'll make a notebook of a little tutorial of, here's the basic
functions and what they do, and then I'll send them out, and then people will
give me feedback on them, or have some new feature, or I'll realize something's
wrong, and then I'll go back and change it and update that page, but then what
happens is people have in the meantime, forked it, and then they have a version
that… and usually what it'll be is actually that I'll have to change a package
as well, so their old fork stops working, and then they complain, and then, oh
no, you have to go get the original [notebook]. Yeah, that's the sort of.. This
probably bites me more than other people, because I'm doing development so
things are changing as they're looking at the code. Like, iotools, a lot of the
functions change names or change syntax.''

>>>>

\subsection{Sharing of results}
Sharing of notebooks is the core feature of RCloud, and a popular one. All
active users we spoke to praised this feature.

Raif says ``I've been sharing my notebooks in order for other people to see what
I've done. It's very convenient for that purpose, I would say.'' ``we haven't
been editing them together, but we've been just sharing, and I've been looking
at things that other people do. So there's no collaborative aspect of it, like
developing the code, but there's sharing aspects for other people to see and for
me to see other people's notebooks''

By default, all notebooks are publicly visible in RCloud, and notebooks can be
found through the notebook tree or search. However, the method for sharing that
users mentioned most is by sending links through email. Clint says, ``I can
share [my notebook] with people and copy it pretty readily. So if my supervisor
wants to see what I've done or QA it, I can just send her a link.''

Besides providing a way to present work to others, notebook sharing can also
provide a starting point. Clint says, ``I think the best part about it is how
easily you can share code... you can find a working example, rather than wearing
out Google and finding questionable examples that may or may not work.'' Raif
notes, if ``some person has done something similar, then you're able to just
edit that, and that's saved a lot of work time for me''

Taylor develops packages for analysts: ``I use it more for sharing code with
other people, and for doing tutorials for iotools or hmr or explaining'' issues with data sources. ``A lot
of times I'll share the code because I'm doing so much package development. I
want people to see how the package works, so I clearly want them to see the
code... I kind of write it just like I would write GitHub Markdown, where you have
little code snippets and text, but RCloud lets me actually run the snippets''
and display the results.

@@

%% Corey: ``being able to share notebooks or codes, or collaborate on something,
%% easily being able to share that information. That's an obvious advantage and
%% nice to have.''

%% Rick: ``I like being able to look at other people's notebooks.''

@@

Taylor: ``I'll make a notebook of a little tutorial of, here's the basic
functions and what they do, and then I'll send them out, and then people will
give me feedback on them, or have some new feature, or I'll realize something's
wrong, and then I'll go back and change it and update that page, but then what
happens is people have in the meantime, forked it, and then they have a version
that... and usually what it'll be is actually that I'll have to change a package
as well, so their old fork stops working, and then they complain, and then, oh
no, you have to go get the original [notebook]. Yeah, that's the sort of... This
probably bites me more than other people, because I'm doing development so
things are changing as they're looking at the code. Like, iotools, a lot of the
functions change names or change syntax.''
